Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-08-14 tex/MesnardoBarba2019.tex
Add references to reviewers' comments
Mention ECC-enabled in caption of Table 1

\begin{table*}[b]
    \renewcommand{\arraystretch}{1.5}
    \caption{Hardware specifications of nodes used on Microsoft Azure and Colonial One. On both platforms, MPI applications take advantage of RDMA (Remote Direct Memory Access) network with FDR InfiniBand.}
    \label{tab:hw_specs}
    \centering
    \begin{tabular}{cccccccc}
        Platform & Node & Intel Xeon CPU & \# threads & NVIDIA GPU & RAM (GiB) & SSD Storage (GiB) \\
        \hline
        \multirow{2}{*}{Azure} & \texttt{NC24r} & Dual 12-Core E5-2690v3 (2.60GHz) & 24 & 4 x K80 & 224 & 1440 \\
        & \texttt{H16r} & Dual 8-Core E5-2667v3 (3.20GHz) & 16 & - & 112 & 2000 \\
        \hline
        \multirow{2}{*}{Colonial One} & \texttt{Ivygpu} & Dual 6-Core E5-2620v2 (2.10GHz) & 12 & 2 x K20 & 120 & 93 \\
        & \texttt{Short} & Dual 8-Core E5-2650v2 (2.60GHz) & 16 & - & 120 & 93 \\
        \hline
    \end{tabular}
\end{table*}

@@

This work was possible thanks to a sponsorship from the Microsoft Azure for Research program\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} and supported by NSF Grant No. CCF-1747669.
We would like to thank Kenji Takeda, Fred Park, and Joshua Poulson of Microsoft for their help.

>>>>

\begin{table*}[b]
    \renewcommand{\arraystretch}{1.5}
    \caption{Hardware specifications of nodes used on Microsoft Azure and Colonial One. On both platforms, MPI applications take advantage of RDMA (Remote Direct Memory Access) network with FDR InfiniBand and ECC is enabled for GPU computing.}
    \label{tab:hw_specs}
    \centering
    \begin{tabular}{cccccccc}
        Platform & Node & Intel Xeon CPU & \# threads & NVIDIA GPU & RAM (GiB) & SSD Storage (GiB) \\
        \hline
        \multirow{2}{*}{Azure} & \texttt{NC24r} & Dual 12-Core E5-2690v3 (2.60GHz) & 24 & 4 x K80 & 224 & 1440 \\
        & \texttt{H16r} & Dual 8-Core E5-2667v3 (3.20GHz) & 16 & - & 112 & 2000 \\
        \hline
        \multirow{2}{*}{Colonial One} & \texttt{Ivygpu} & Dual 6-Core E5-2620v2 (2.10GHz) & 12 & 2 x K20 & 120 & 93 \\
        & \texttt{Short} & Dual 8-Core E5-2650v2 (2.60GHz) & 16 & - & 120 & 93 \\
        \hline
    \end{tabular}
\end{table*}

@@

This work was possible thanks to a sponsorship from the Microsoft Azure for Research program\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} and supported by NSF Grant No. CCF-1747669.
We would like to thank Kenji Takeda, Fred Park, and Joshua Poulson of Microsoft for their help.
We are also immensely grateful to the reviewers, Patrick O'Leary \cite{oleary_2019} and Freddie Witherden \cite{witherden_2019}, for their suggestions.
